Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays

### 2019-12-18 review_article.Rmd
viridis reference

Choropleth maps colour each geographic unit to allow map users to measure the value of the statistic [@EI]. Map users contrast the colours in neighbouring areas to understand the spatial distribution. Map creators must choose an effective colour scheme, but it is a difficult task [@CB]. The ColorBrewer system supports map creators in the decision making process, but this does not full provide perceptual colour specifications. When communicating information using colour, a map creator should use a scheme that has a linear color gradient, with perceptually uniform color spaces to convey that equal steps in data align with equal steps in the colour scheme [@PUCS].

The use and colors of borders and backgrounds can also change the appearance of the colors representing the value of the statistics [@CB]. These supports are important, though, to allow a reference point to orient users to the geographic regions.

>>>>

Choropleth maps colour each geographic unit to allow map users to measure the value of the statistic [@EI]. Map users contrast the colours in neighbouring areas to understand the spatial distribution. The ColorBrewer system [@CB] and viridis [@viridis] palettes provide effective colour schemes for qualitative, sequential and diverging data. When communicating information using colour, a map creator should use a scheme that has a linear color gradient, with perceptually uniform color spaces that match equal steps in data space with equal steps in the colour space [@PUCS]. 
The use of borders and backgrounds, and their colours, can also change the appearance of the colors representing the value of the statistics [@CB]. These supports can be used to implement a reference point in the colour scheme as well as orient users to the geographic regions.
